% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Theodore Bauer}
\newcommand{\CVTitle}{}
\newcommand{\CVNote}{}
\newcommand{\CVWebpage}{github.com/tedbauer}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
tjb272@cornell.edu
\,\SubBulletSymbol\,
github.com/tedbauer
\,\SubBulletSymbol\,
\,(832)\,330-5858
\end{SubTitle}

\begin{Body}
%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
{\textbf{Cornell University, College of Arts and Sciences}},
Ithaca, NY
\Gap
\BulletItem
B.A. in Computer Science
\hfill
Expected May 2019
\begin{Detail}
\SubBulletItem
GPA: 3.50 / 4.00
\SubBulletItem
Selected Coursework: Programming Languages and Logics, Functional Programming, \newline Operating Systems (with Practicum), Object-Oriented Programming, Discrete Structures, \newline Computer System Organization, Analysis of Algorithms, Database Systems, \newline Probability Models and Inference, Seminar in Programming Languages
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%
%% CAMPUS ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Skills}
{}
{}

\textbf{General Programming:} Python, OCaml, C, Java, C++
\Gap
\textbf{Web Development:}  PHP, SQL, HTML/CSS, JavaScript, Bootstrap
\Gap
\textbf{Tools:} Git, Vim, CircleCI, Shell Scripting, \LaTeX, Make, Dune, Gradle

\Section
{Experience}{}{}

\Entry
\textbf{Undergraduate Researcher,} Cornell Capra Research Group
\hfill Mar. 2018 - Present
\Gap

\begin{Detail}
\BulletItem Designed language semantics and type system for Seashell, a hardware \newline programming language, advised by Professor Adrian Sampson
\BulletItem Implemented compiler from scratch with OCaml
\BulletItem Proved correctness of memory access language construct
\BulletItem Wrote Vim syntax highlighting plugin

\end{Detail}

\Gap

\Entry
\textbf{Software Engineering Intern,} Rev: Ithaca Startup Works
\hfill
Oct. 2016 -- Aug. 2017
\Gap
\begin{Detail}
\BulletItem
Worked on technical staff for 11 week Cornell-run Rev Hardware Accelerator
\BulletItem
Developed hardware/software prototyping workshop for entrepreneurs showcasing \newline "toy" IoT product development; built communication device with a Particle Photon \newline board that interfaced with an Apache/MySQL/PHP server application
\end{Detail}
\Section{Projects}{}{}

\BulletItem
\textbf{``A Lonely Alpaca" puzzle video game}
\hfill
Aug. 2018 - Dec. 2018
\begin{Detail}
\Item
Implemented with Unity and C\# alongside 2 other developers and 2 designers
\SubBulletItem Non-exclusive license for game purchased by Coolmath Games
\SubBulletItem Recognized on front page of Newgrounds.com
\end{Detail}


\Gap
\BulletItem
\textbf{EG Operating System abstractions}
\hfill
Aug. 2018 - Dec. 2018
\begin{Detail}
\Item
Implemented in C:
\SubBulletItem A fully-featured FAT filesystem
\SubBulletItem A user-level threading and semaphore interface
\SubBulletItem A multiprocess interface with a multi-level feedback queue
\end{Detail}

\Gap

\BulletItem
\textbf{``Home Away from Gnome" pseudo-3D video game}
\hfill
Dec. 2018 - Jun. 2018
\begin{Detail}
\Item
Designed and implemented with Java, libGDX and Gradle alongside 3 other developers \newline and 2 designers over the course of one semester for the Cornell Game Design Initiative
\end{Detail}

\Gap
\BulletItem
\textbf{``Pandemic" turn-based game with GUI}
\hfill
Aug. 2017
\begin{Detail}
\Item
Implemented multiplayer board game with OCaml and Lablgtk with 3 other developers
\end{Detail}

\Gap
\BulletItem
\textbf{Yacgb Game Boy emulator}
\hfill
Feb. 2019
\begin{Detail}
\Item
Implemented with C and SDL2; features simulated CPU and GPU
\end{Detail}


\Section{Teaching}{}{}

\BulletItem CS 2043: Unix Tools and Scripting (TA) \hfill Spring 2019
\BulletItem CS 3110: Functional Programming and Data Structures (TA) \hfill Spring 2018, Fall 2018
\BulletItem CS 4410: Operating Systems (TA) \hfill Summer 2018
\BulletItem CS 1110: Introduction to Computing with Python (Consultant) \hfill Fall 2017

\Section
{Awards}{}{}
\BulletItem
\textbf{ELI Research Award}, to fund Seashell, a hardware accelerator language
\hfill
Jun. 2018

\BulletItem
\textbf{Teaching Assistant Award}, for outstanding contributions to CS 3110 staff
\hfill
Aug. 2018

\Section
{Campus Involvement}{}{}

\BulletItem
\textbf{Mary Donlon Hall Resident Advisor (RA)}
\hfill
Jun. 2016 - May 2018

\BulletItem
\textbf{Association of CS Undergraduates (ACSU) Mentor}
\hfill
Aug. 2018 - Present

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\end{Body}

\end{document}
